\subsection{Language choice}


\subsubsection{Java}

Java is one of the most widely used language fro development. It also
has the unique advantage that Java programs compiles to a Java bytecode,
which runs on a Java Virtual Machine. This means that as a developer
they would only usually have to create the program once and it would
run on most machines. 

Java also happens to be the native language for Android, making it
an ideal choice of language for an Android developer. Android platform
has a market share of around 81.5\%\cite{market-share}. Which means
creating a library for android made the perfect sense. More people
are likely to have an Android device during a meeting and also there
is a more likely hood that there would a lot more spare Android devices
which can be used to create the screen for the table. Android devices
are also extremely cheap which means even if the users had to buy
some devices to use the interactive table it would be relatively cheap.

By creating the library in Java there would be more likely hood for
adoption by other users due to the ease in which someone could pick
it up and also due to the large number of Android developers other
there already. There are lot of vendors that produce cheap Android
devices\cite{cheap-android}. 

One of the biggest disadvantage of using Android devices with BLE
technology is the the Android Bluetooth Crash bug\cite{bluetooth-share}.
There is a bug in Bluetooth stack of Android where an Android device
can only see 1,990 different Bluetooth MAC addresses before the Android
BluetoothService crashes. Android also periodically saves its list
of recent mac address which means this stored list could get filled
up pretty quickly. Small iBeacons such as the Gimbal by Qualcomm generates
a new MAC address for itself every 0.8 seconds which means this list
could get filled very quickly. When is this list gets filled up an
error dialogue saying \textquotedbl{}Unfortunately, Bluetooth Share
has Stopped\textquotedbl{} shows up. The only real solution to this
problem is a downloading an application called Bluetooth Crash Resolver by radius
network which is not a perfect solution but the best there is right
now.


\subsubsection{Object C/Swift}

Object C/ Swift is native language for iOS platform used by the Apple
devices. With a 14.8\% market share iOS is the second biggest mobile
platform out there\cite{market-share}. They recently brought out
another language called Swift which is also another language that
could used for development in the iOS platform. iOS was a platform
that was brought in 2007 and over the last 8 years, over one billion
iOS devices has been sold\cite{oneBios}.

Over 1.4 million iOS applications has been published in Apples App
store, showing that large number of developers has adopted Apple products
and are creating Apps for the platform. Apple is also the company
the coined the term iBeacon which are a ``new class of low-powered,
low-cost transmitters that can notify nearby iOS 7 or 8 devices of
their presence.'' This means that iOS platform has a more mature
codebase for BLE technology and also there are a lot more support
for it. The iOS CoreLocation\cite{corelocation} framework is a relatively
more accurate feature giving iOS a very good advantage while working
with BLE technology. The Bluetooth stack used by Apple product is
a much more efficient one.

However for a developer there quite a lot of requirements before being
able to develop for an Apple platform. Unlike Android development
an iOS developer needs to have an Apple computer and a Apple developer
License before they can create apps for the platform, neither of which
are cheap. Apple devices are also rather expensive to buy and there
fore unlike for people to have it just laying around.


\subsubsection{JavaScript}

JavaScript is also another viable language for creating applications
for mobile devices especially since the introduction of frameworks
such as PhoneGap\cite{phonegap} and Ionic\cite{ionic}. Mobile Frameworks
such as these work on top Apache Cordova which allows developers to
create a application using web technologies such as HTML5, CSS3 and
JavaScript instead of using the platform specific APIs like those
in iOS and Android. Cordova wraps these web application to work on
different devices. These applications are called Hybrid applications
since they are not truly native mobile application or web application.

The use of web-based technologies leads many PhoneGap applications
to run slower than native applications with similar functionality.
However PhoneGap supports development for iOS, Blackberry, Android,
LG webOS, Microsoft Windows Phone (7 and 8), Nokia Symbian OS, Tizen
(SDK 2.x), Bada, Firefox OS, and Ubuntu Touch making it one of the
best language to use while creating an application to get the most
exposure for the library. it also supports most of the features of
a phone that a native language does as well like Accelerometer, Compass
etc as shown in \ref{tab:PhoneGap-table}.
\todo[inline]{Language: fix Table}

\subsection{Summary}
After careful consideration of the available options I had for each choices. I decided to go with Java as my language choice and Android as my platform. Mainly due to my familiarity with both as well as the fact that android devices have a larger market share, therefore more people are likely to have one in their possession.  I decided to use OpenCV as my vision library due to its cross platform availability and also because it worked on all hardware. It also had the added bonus of being the more mature library out of the two choices.

I decided to use contour detectoin and colour detection for my main graphics manipulation and device identification, because both were less resource intensive algorithm. This meant that it was the most efficient of the choices I had due to the limited resources of the devices. Using something that worked well with less powerful processor and smaller memory was one of the priority of this project.

I also decided to use firebase as the Data storage part of my algorithm because of its real time aspects of the library. The opportunity to get real time update and push data from the storage without having to worry about concurrency issues wes too good to pass.

